\documentclass[sigconf,table,screen,xcdraw,review]{acmart}

\usepackage{booktabs} 
\usepackage{framed}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{pifont}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{xcolor,colortbl}
\usepackage{hhline}
\usepackage{adjustbox}
\usepackage{booktabs} 
\usepackage{amssymb}
\usepackage{balance}
\usepackage{tcolorbox}
\usepackage{url}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{amssymb}
\usepackage{standalone}
\usepackage{url}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.73,0.38,0.06}
\definecolor{codepurple}{rgb}{0.27,0.38,0.97}
\definecolor{codemagenta}{rgb}{0.74,0.09,0.42}
\definecolor{backcolour}{rgb}{0.96,0.96,0.96}

% for footnotes on the same line
\usepackage[para]{footmisc}
\setcitestyle{numbers,sort&compress}

\newcommand\iris{\textsc{DisDrillery}\xspace}

\newcommand*{\ColorIfNotInString}[1]{\color{codegray}\textbf{#1}}%

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{codepurple},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codemagenta},
    language=Java,
    breakatwhitespace=false,         
    breaklines=true,                 
    keepspaces=true,                 
    numbers=left,
    xleftmargin=0.25cm,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=1,
    frame=tb,
    framerule=0pt,
    literate=%
    {0}{{{\ColorIfNotInString{0}}}}1
    {1}{{{\ColorIfNotInString{1}}}}1
    {2}{{{\ColorIfNotInString{2}}}}1
    {3}{{{\ColorIfNotInString{3}}}}1
    {4}{{{\ColorIfNotInString{4}}}}1
    {5}{{{\ColorIfNotInString{5}}}}1
    {6}{{{\ColorIfNotInString{6}}}}1
    {7}{{{\ColorIfNotInString{7}}}}1
    {8}{{{\ColorIfNotInString{8}}}}1
    {9}{{{\ColorIfNotInString{9}}}}1
}
% \usepackage{inconsolata}
\lstset{basicstyle=\fontsize{6}{6}\fontfamily{\ttdefault}\selectfont,style=mystyle}

\renewcommand{\arraystretch}{1.2}

\usepackage{hyperref}
\usepackage{cleveref}

\include{macro}

\acmConference[MaLTeSQuE 2020]{MaLTeSQuE 2020: International Workshop on Machine Learning Techniques for Software Quality Evaluation}{November 13, 2020}{Sacramento, USA}
\acmBooktitle{MaLTeSQuE 2020: International Workshop on Machine Learning Techniques for Software Quality Evaluation, November 13, 2020 - Sacramento, USA}
\acmPrice{15.00}
\acmISBN{978-1-4503-9999-9/18/06}

\sloppy

\begin{document}

\title[Speeding Up the Data Extraction of Machine Learning Approaches]{Speeding Up the Data Extraction of Machine Learning Approaches: A Distributed Framework}
% \iris stays for d\textbf{I}st\textbf{R}ibuted m\textbf{I}ning \textbf{S}oftware repositories

	\author{Martin Steinhauer}
	\affiliation{%
		\institution{SeSa Lab - University of Salerno}
		\city{Fisciano (Salerno)}
		\state{Italy}
	}
	\email{m.steinhauer@studenti.unisa.it}

	\author{Fabio Palomba}
	\affiliation{%
	\institution{SeSa Lab - University of Salerno}
	\city{Fisciano (Salerno)}
	\state{Italy}
	}
	\email{fpalomba@unisa.it}

\begin{abstract}
In the last decade, mining software repositories (MSR) has become one of the most important sources to feed machine learning models. Especially open-source projects on platforms like GitHub are providing a tremendous amount of data and make them easily accessible. Nevertheless, there is still a lack of standardized pipelines to extract data in an automated and fast way. Even though several frameworks and tools exist which can fulfill specific tasks or parts of the data extraction process, none of them allow neither building an automated mining pipeline nor the possibility for full parallelization. As a consequence, researchers interested in using mining software repositories to feed machine learning models are often forced to re-implement commonly used tasks leading to additional development time and libraries may not be integrated optimally. 

This preliminary study aims to demonstrate current limitations of existing tools and Git itself which are threatening the prospects of standardization and parallelization. We also introduce the multi-dimensionality aspects of a Git repository and how they affect the computation time. Finally, as a proof of concept, we define an exemplary pipeline for predicting refactoring operations, assessing its performance. Finally, we discuss the limitations of the pipeline and further optimizations to be done.\end{abstract}

\keywords{Machine Learning Pipelines; Distributed Mining; Mining Software Repositories.}
\maketitle

\input{introduction}
\input{background}
\input{approach}
\input{study}
\input{discussion}
\input{conclusions}

\balance
\bibliographystyle{abbrv}
\bibliography{references}
% That's all folks!
\end{document}
